---
title: "Final Project - Developing data products"
author: "Facundo Perez"
date: "27/4/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## App for explore data from nba players stats 2018-19

The app can be found in [link](https://coyam11.shinyapps.io/week4_app/)

The dataset consist in the player that avergare more than 30 minutes per game in the nba 2018-19 season.
Look the head
``` {r echo=FALSE, message=FALSE}
nba1819<-read.csv("nba1819.csv")
```

``` {r echo = TRUE, message=FALSE, comment=''}
head(nba1819)
```

## Structure

The app consists in three tabs:

- Plot: Scatter plot of the selected variables, with size points by the third variable. Can be added a linear model
- Table: Table of data with the name of the player, and the three stats that the user has selected
- Documentation: A series of steps for understand the functionality of the app


## Example Plot

1. Select Turnovers in x axis
2. Select Asists on y axis
3. Select Points for points size 
4. Check the box for set linear model

``` {r echo=FALSE, message=FALSE, fig.align='center', warning=FALSE}
library(ggplot2)
library(plotly)
library(dplyr)
g <- ggplot(nba1819, aes(Turnovers, Asists))
g <- g + geom_point(aes(size=Points, label_value=Player), colour="darkgreen", alpha=0.7)
g <- g + geom_smooth(method='lm', col="blue")
g <-ggplotly(g)
g
```

### Table output

``` {r echo = FALSE, message= FALSE, warning=FALSE, comment='', fig.align='left'}
nba1819[1:10,c("Player", "Turnovers", "Asists", "Points")]

```

## Look at the server functionality

``` {r echo=TRUE, eval=FALSE}
shinyServer(function(input, output) {
    dataInput <- reactive({
        nba1819[,c("Player", input$X, input$Y, input$S)]
        })
    output$tabla1 <- renderTable({dataInput()})
     output$Scatplot <- renderPlotly({
          g<- ggplot(dataInput(), aes(dataInput()[,2], dataInput()[,3]))
          g <- g + geom_point(aes(size=dataInput()[,4], label_value=Player), colour="darkgreen", alpha=0.7)
          g <- g + labs(x=colnames(dataInput())[2], y=colnames(dataInput()[3]))  
          if(input$fit){
           g <- g + geom_smooth(method='lm', col="blue")
           }
         ggplotly(g)
         })
})
```